Supplemental Material for submission ``Do Objects in Real-World Images Have a Canonical Name?''

### 2019-05-21 papers/EMNLP2019/analysis.tex
examples for relations in table

\begin{table}
\small
\centering
\begin{tabular}{lcc}
\toprule
         relation & \% types & \% token \\
\midrule
% meronym &  0.1 &  0.2 \\
% holonym &  0.1 &  0.4 \\
 word-not-covered &  10.6 &  2.6 \\
\midrule
 synonym &  1.1 &  1.1 \\
 hyponym &  2.2 &  3.8 \\
 co-hyponym &  3.1 &  5.9 \\
 hypernym &  10.5 &  27.7 \\
 rel-not-covered &  72.2 &  58.3 \\
\bottomrule
\end{tabular}
\caption{Lexical relations of naming variants in ManyNames to annotated \vg synset, averaged over synsets.}
\label{tab:rel}
\vspace{-0.5cm}
\end{table}

>>>>

\begin{table}
\small
\centering
\setlength{\tabcolsep}{2pt}
\begin{tabular}{lcc|p{2.5cm}}
\toprule
         relation & \% types & \% token & \it ex: jacket \\
\midrule
% meronym &  0.1 &  0.2 \\
% holonym &  0.1 &  0.4 \\
 word-not-covered &  10.6 &  2.6 & \it outdoor vest\\
\midrule
 synonym &  1.1 &  1.1 & \it hoodie  \\
 hyponym &  2.2 &  3.8 & \it parka, blazer \\
 co-hyponym &  3.1 &  5.9 & \it raincoat\\
 hypernym &  10.5 &  27.7 & \it clothing, coat\\
 rel-not-covered &  72.2 &  58.3 & \it sweatshirt, man\\
\bottomrule
\end{tabular}
\caption{Lexical relations of naming variants in ManyNames to annotated \vg synset, averaged over synsets.}
\label{tab:rel}
\vspace{-0.5cm}
\end{table}
